Tampering Detection In Low-Power Smart Cameras

### 2015-05-26 paper.tex
Rimessa la segmentazione...

>>>>

When the feature vectors are computed for all the pixels we start the segmentation phase.
This is made using classical clustering techniques:
in particular we use a modified version of the classical k-means algorithm \cite{han2006data}. 
In this implementation, each feature vector belongs to a cluster if its \textit{weighted Minkowski distance} \cite{de2012minkowski} from the cluster's centroid is minimum with respect to the distance from the other centroids. 
The distance is weighted considering the standard deviation of each elements of the feature vectors inside each cluster \cite{kottke1994motion}, in order to consider, during the clustering, also the contribute of the fields which have low variance. \ad{Giacomo: prova a vedere se si capisce cosa voglio dire in queste frasi!!!}
